### 2023-07-21 main.tex
fixed

		D_{j,j}(x)B_{i}(y)&=B_{i}(x)D_{j,j}(y)+\frac{1}{2}h_{3}(x,y)\left(B_{i}(x)D_{i,i}(y)+B_{i}(y)D_{N,N}(x)\right)
		\\&-
		\frac{1}{2}h_{3}(x,y)\left(B_{i}(y)D_{i,i}(x)+B_{i}(x)D_{N,N}(y)\right)

@@

		h_{1}(x,y)\sum_{k=1\,:\, k\neq i}^{N-1}\left(B_{k}(x)D_{k,i}(y)-B_{k}(y)D_{k,i}(x)\right)
	&f(x,y)=\frac{(x+y)(x-y-1)}{(x-y)(1+x+y)}&f_{1}(x,y)=\frac{(x+y)}{(x-y)(1+x+y)}\quad&f_{2}(x,y)=\frac{1}{(1+x+y)}\nonumber\\&h(x,y)=\frac{(1+x-y)(x+y+2)}{(x-y)(1+x+y)}
	&h_{1}(x,y)=-\frac{(x+y+2)}{(x-y)(1+x+y)}\quad&h_{2}(x,y)=\frac{(2+x-y)}{(x-y)(1+x+y)}\nonumber
	\\&h_{3}(x,y)=\frac{2}{(x-y)(1+x+y)}
\subsection{Charges}
Then we have
		T^{\Delta}(x)=tr_{0}&\left(\begin{pmatrix}
		\end{pmatrix}\right.
		\\& \left.
		\;\;\;\begin{pmatrix}
		\end{pmatrix}\right)
Therefore we can write the polynomial expansion
		T^{\Delta}(x)=&
		(N+x)D_{N,N}(x)-\sum_{i=1}^{N-1}xD_{ii}(x)+\sum_{i=1}^{N-1}(2x+N)(\alpha_{i}-\beta_{i})B_{i}(x)=
		\sum_{k=0}^{2L+2}Q_{k}x^{k}
We call these $Q_{k}$, with $k=0,\ldots,2L+2$, the \textit{charges}. \\
We can also introduce 
	T_{0}(x)=(N+x)D_{N,N}(x)-\sum_{i=1}^{N-1}xD_{ii}(x)\quad\text{such that}\quad T_{\Delta}(x)=T_{0}(x)+\sum_{i=2}^{N}(2x+N)(\alpha_{i}-\beta_{i})B_{i}(x)
\end{equation}For large $x$, we compute them by expanding $U_{0}^{d}(x)$ in a polynomial: 
	D_{N,N}(x)=\sum_{a=0}^{2L+1}D_{N,N}^{a}x^{a}\quad D_{ii}(x)=\sum_{a=0}^{2L+1}D_{ii}^{a}x^{a}\quad B_{i}(x)=\sum_{a=0}^{2L-1}B_{i}^{a}x^{a}
The coefficients that we need are the following:
	D_{N,N}(x)=D_{N,N}^{2L+1}x^{2L+1}+D_{N,N}^{2L}x^{2L+1}+D_{N,N}^{2L-1}x^{2L-1}+\ldots
	D_{N,N}^{2L+1}=I^{tot}
	D_{N,N}^{2L}=I^{tot}+2e_{NN}^{tot}
		D_{N,N}^{2L-1}=3e_{NN}^{tot}-\sum_{j=1}^{N-1}e_{jj}^{tot}+2\sum_{a\neq b}e_{NN}^{[a]}e_{NN}^{[b]}
{\color{blue}ok}

>>>>

		D_{j,j}(x)B_{i}(y)&=B_{i}(x)D_{j,j}(y)+\frac{1}{2}h_{3}(x,y)\left(B_{i}(y)D_{i,i}(x)-B_{i}(x)D_{i,i}(y)\right)

@@

		\frac{1}{2}h_{3}(x,y)\left(B_{i}(x)D_{N,N}(y)-B_{i}(y)D_{N,N}(x)\right)
	h_{1}(x,y)\left(B_{j}(x)D_{j,i}(y)-B_{j}(y)D_{i,j}(x)\right)
	\frac{1}{2}h_{3}(x,y)\sum_{k=1\,:\,k\neq i,j}\left(B_{k}(y)D_{k,i}(x)-B_{k}(x)D_{k,i}(y)\right)

\end{itemize}
where
\begin{align}
	&f(x,y)=\frac{(x+y)(x-y-1)}{(x-y)(1+x+y)}&f_{1}(x,y)=\frac{(x+y)}{(x-y)(1+x+y)}\quad&f_{2}(x,y)=\frac{1}{(1+x+y)}\nonumber\\&h(x,y)=\frac{(1+x-y)(x+y+2)}{(x-y)(1+x+y)}
	&h_{1}(x,y)=-\frac{(x+y+2)}{(x-y)(1+x+y)}\quad&h_{2}(x,y)=\frac{(2+x-y)}{(x-y)(1+x+y)}\nonumber
	\\&h_{3}(x,y)=\frac{2}{(x-y)(1+x+y)}
\end{align}
\subsection{Charges}
Then we have
\begin{equation}
	\begin{split}
		T^{\Delta}(x)=tr_{0}&\left(\begin{pmatrix}
			-x&0&0&\ldots&0&(N+2x)(\alpha_{1}-\beta_{1})\\
			0&-x&0&\ldots&0&(N+2x)(\alpha_{2}-\beta_{2})\\
			\vdots&\vdots&\ddots&\vdots&\vdots&\vdots\\
			0&0&0&\ldots&-x&(N+2x)(\alpha_{N-1}-\beta_{N-1})\\
			0&0&0&\ldots&0&1+x
		\end{pmatrix}\right.
		\\& \left.
		\;\;\;\begin{pmatrix}
			D_{1,1}(x)&D_{1,2}(x)&\ldots&D_{1,N-1}(x)&C_{1}(x)\\
			D_{2,1}(x)&D_{2,2}(x)&\ldots&D_{2,N-1}(x)&C_{2}(x)\\
			\vdots&\vdots&\ddots&\vdots&\vdots\\
			D_{N-1,1}&D_{N-1,2}&\ldots&D_{N-1,N-1}(x)&C_{N-1}\\
			B_{1}(x)&B_{N-1}(x)&\ldots&D_{N,N-1}(x)&D_{N,N}(x)
		\end{pmatrix}\right)
	\end{split}
\end{equation}
Therefore we can write the polynomial expansion
\begin{equation}
	\begin{split}
		T^{\Delta}(x)=&
		(N+x)D_{N,N}(x)-\sum_{i=1}^{N-1}xD_{ii}(x)+\sum_{i=1}^{N-1}(2x+N)(\alpha_{i}-\beta_{i})B_{i}(x)=
		\sum_{k=0}^{2L+2}Q_{k}x^{k}
	\end{split}
\end{equation}
We call these $Q_{k}$, with $k=0,\ldots,2L+2$, the \textit{charges}. \\
We can also introduce 
\begin{equation}
	T_{0}(x)=(N+x)D_{N,N}(x)-\sum_{i=1}^{N-1}xD_{ii}(x)\quad\text{such that}\quad T_{\Delta}(x)=T_{0}(x)+\sum_{i=2}^{N}(2x+N)(\alpha_{i}-\beta_{i})B_{i}(x)
\end{equation}For large $x$, we compute them by expanding $U_{0}^{d}(x)$ in a polynomial: 
\begin{equation}
	D_{N,N}(x)=\sum_{a=0}^{2L+1}D_{N,N}^{a}x^{a}\quad D_{ii}(x)=\sum_{a=0}^{2L+1}D_{ii}^{a}x^{a}\quad B_{i}(x)=\sum_{a=0}^{2L-1}B_{i}^{a}x^{a}
\end{equation}
The coefficients that we need are the following:
\begin{equation}
	D_{N,N}(x)=D_{N,N}^{2L+1}x^{2L+1}+D_{N,N}^{2L}x^{2L+1}+D_{N,N}^{2L-1}x^{2L-1}+\ldots
\end{equation}
where 
\begin{equation}
	D_{N,N}^{2L+1}=I^{tot}
\end{equation}
\begin{equation}
	D_{N,N}^{2L}=I^{tot}+2e_{NN}^{tot}
\end{equation}
\begin{equation}
	\begin{split}
		D_{N,N}^{2L-1}=3e_{NN}^{tot}-\sum_{j=1}^{N-1}e_{jj}^{tot}+2\sum_{a\neq b}e_{NN}^{[a]}e_{NN}^{[b]}
	\end{split}
\end{equation}
{\color{blue}ok}
